---
title: "Project_Computation"
author: "Mansi Darji"
date: "12/11/2021"
output: 
  html_document:
    code_folding: show
    theme: journal
    toc: yes
    to _float: yes
  word_document:
    toc: yes
---


## Section-1: Introduction
  ## 1) Introduction of the paper
  ## 2) Introduction of each test
    ## Touch on the theory, maybe not as in-depth as the paper however
  ## 3) Introduce the types of distributions and how we generate the random            variates
  ## 4) Talk about the power of each test and how it is defined 

## Section-2: Results
  ## Grabbing critical values
  ## Writing the code for the tests
    ## Specify difficulties with the tests and any changes made.
  ## Introduce by order in the paper (the table/figures) and then comment on        the difficulties associated with each test and distribution. 
      ## Make a comment on anything that did not match.
  ## Summarize the results of the paper
  
## Section-3: Summary
  ## Talk about our own insights, whether we agree with the paper's conclusion,   and the highlights of what we learned while trying to replicate the results o   of the paper. 
## Section-4: Future Work
  ## Discuss how this could apply to future work, both in industry and              academia. 

## References

Yap, Bee Wah, and Chiaw Hock Sim. "Comparisons of various types of normality tests." Journal of Statistical Computation and Simulation 81.12 (2011): 2141-2155.

```{r}
citation(package = "fBasics")
```

```{r}
citation(package = "normtest")
citation(package = "lawstat")
```

## Appendix

